Validating Cell Tower Clustering for Mobility Prediction

### 2012-12-12 docs/paper589.tex
typo

There are two main papers that tackle the problem of oscillation effects: the Mobility Profiler paper, by Bayir et al. \cite{mobilityprofiler}, and the Leap Graph paper by Duffield et al \cite{LeapGraph}. Ideally we would want to evaluate both of them, but the leap graph algorithm, which was published by resarchers at AT\&T, makes use of the active set of connections. The active set contains all towers that are within range of the phone's antenna at any given time. Unfortunately, active set logs are not public which makes it impossible for us to evaluate the leap graph algorithm.

>>>>

There are two main papers that tackle the problem of oscillation effects: the Mobility Profiler paper, by Bayir et al. \cite{mobilityprofiler}, and the Leap Graph paper by Duffield et al \cite{LeapGraph}. Ideally we would want to evaluate both of them, but the leap graph algorithm, which was published by researchers at AT\&T, makes use of the active set of connections. The active set contains all towers that are within range of the phone's antenna at any given time. Unfortunately, active set logs are not public which makes it impossible for us to evaluate the leap graph algorithm.
